{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-14 thesis/tm.tex
more tm tests

\begin{figure}[h]
        \begin{center}
        \begin{tabular}{ll}
		\multicolumn{2}{c}{Initially {\tt \ctype{int} foo, bar = \const{0}; \ctype{mutex\_t} m;}} \\
                \\
                \begin{tabular}{l}
                {\bf Thread 1} \\
                \hline
			\texttt{\flow{if} (\call{\_xbegin}() == \const{STARTED}) \{} \\
			\texttt{~~~~foo++;} \\
			\texttt{~~~~\call{\_xend}();} \\
			\texttt{\} \flow{else} \{} \\
			%\texttt{~~~~\call{mutex\_lock}(\&m);} \\
			\texttt{~~~~\flow{assert}{}(foo + bar < \const{2});} \\
			%\texttt{~~~~\call{mutex\_unlock}(\&m);} \\
			\texttt{\}} \\
                \end{tabular}
                &
                \begin{tabular}{l}
                {\bf Thread 2} \\
                \hline
			\texttt{\flow{if} (\call{\_xbegin}() == \const{STARTED}) \{} \\
			\texttt{~~~~bar++;} \\
			\texttt{~~~~\call{\_xend}();} \\
			\texttt{\} \flow{else} \{} \\
			%\texttt{~~~~\call{mutex\_lock}(\&m);} \\
			\texttt{~~~~\flow{assert}{}(foo + bar < \const{2});} \\
			%\texttt{~~~~\call{mutex\_unlock}(\&m);} \\
			\texttt{\}} \\
                \end{tabular}
        \end{tabular}
        \end{center}
	\caption{Motivating example for retry independence reduction.}
	\label{fig:retry-set-example}
\end{figure}

@@

			& 2,1 & \cpu{28.40} 	& \ints{150} 	& \cpu{94}	& \ints{26.55}	& \cpu{14.88}	& \ints{9} \\

@@

\begin{table}[t]
	\begin{center}
		\footnotesize
		\begin{tabular}{cc}
		\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf STM ({\tt -A -S})} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em est.}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.41} & \ints{4} \\
			({\tt spinlock})
			& 2,2 & \cpu{198.77} & \ints{1702} \\
			% if lock(spin_fixed) will time out on 2,3 and 3,2, this is guaranteed to aswell
			& 3,1 & \cpu{35.28} & \ints{246} \\
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.55} & \ints{4} \\
			({\tt spin\_fixed})
			& 2,2 & \cpu{105.57} & \ints{998} \\
			& 2,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 3,1 & \cpu{28.27} & \ints{186} \\
			& 3,2 & \ETAdag{13y 281d} & \ETAdag{1443676} \\
			% [JOB 4] progress: 169893/1443676 brs (11.768080%), ETA 13y 280d 17h 30m 54s (elapsed 9h 59m 48s)
			& 4,1 & \ETAdag{16h 26m} & \ETAdag{432628} \\ % was: 30408, 282084 pre mkrun
			% [JOB 4] progress: 286910/432628 brs (66.317896%), ETA 6h 26m 25s (elapsed 9h 59m 48s)
			% total CPU time consumed: 10h 4s (36004288982 usecs) (core saturation: 12%)
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.44} & \ints{4}		\\
			({\tt mutex})
			& 2,2 & \cpu{16.83} & \ints{180}	\\
			& 2,3 & \cpu{405.21} & \ints{9372}	\\
			& 2,4 & \cpu{qqq} & \ints{qqq}	\\ % was: 15266 sec 384512 pre mkrun
			& 3,1 & \cpu{15.00} & \ints{132}	\\
			%& 3,2 & \cpu{29432.87} & \ints{707086}	\\ % pre mkrun fix (let alone bottom1)
			& 3,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{665.89} & \ints{15064}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.25} & \ints{1}	\\
			({\tt spin\_fixed})
			& 9,9 & \cpu{4.61} & \ints{1}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.19} & \ints{1}	\\
			({\tt mutex})
			& 9,9 & \cpu{4.62} & \ints{1}	\\
			\end{tabular}
			&
			\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf Non-transactional} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt avl\_mutex}
			& 2,1 & \cpu{3.48} & \ints{7} \\
			& 2,2 & \cpu{6.25} & \ints{85} \\
			& 2,3 & \cpu{24.69} & \ints{561} \\
			& 2,4 & \cpu{217.98} & \ints{4984} \\
			& 3,1 & \cpu{8.26} & \ints{129} \\
			& 3,2 & \cpu{1403.46} & \ints{30653} \\
			& 3,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{199.96} & \ints{4488} \\
			& 4,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			\cline{1-4}
			{\tt map\_mutex}
			& 2,1 & \cpu{39.81} & \ints{83} \\
			& 2,2 & \ETAdag{26h 21m} & \ETAdag{1085126} \\
			% [JOB 9] progress: 496530/1085126 brs (45.757812%), ETA 16h 21m 0s (elapsed 9h 59m 38s)
			% total CPU time consumed: 10h 19s (36019507965 usecs) (core saturation: 12%)
			& 3,1 & \ETAdag{173d 17h} & \ETAdag{12572187} \\
			% [JOB 9] progress: 496281/12572187 brs (3.947451%), ETA 173d 6h 38m 55s (elapsed 9h 59m 43s)
			% total CPU time consumed: 10h 20s (36020148608 usecs) (core saturation: 12%)
			\\
			\\
			\\
			\\
			\\
		\end{tabular}
		\\
		\\
		(a) Verifying HTM locks alone.
		&
		(b) Verifying the lock's client code.
		\end{tabular}
	\end{center}
	\caption{Continuation of Table~\ref{tab:tm-verifs},
		demonstrating abstraction reduction \cite{dbug-phdthesis}
		on the {\tt avl\_fixed} and {\tt map\_basic} tests
		by verifying HTM mutex implementations separately.
		Tested with STM semantics, as both lock implementations include a retry loop.}
	\label{tab:tm-verifs2}
\end{table}

>>>>

\begin{figure}[h]
        \begin{center}
        \begin{tabular}{ll}
		\multicolumn{2}{c}{Initially {\tt \ctype{int} foo, bar = \const{0};}} \\
                \\
                \begin{tabular}{l}
                {\bf Thread 1} \\
                \hline
			\texttt{\flow{if} (\call{\_xbegin}() == \const{STARTED}) \{} \\
			\texttt{~~~~foo++;} \\
			\texttt{~~~~\call{\_xend}();} \\
			\texttt{\} \flow{else} \{} \\
			%\texttt{~~~~\call{mutex\_lock}(\&m);} \\
			\texttt{~~~~\flow{assert}{}(foo + bar < \const{2});} \\
			%\texttt{~~~~\call{mutex\_unlock}(\&m);} \\
			\texttt{\}} \\
                \end{tabular}
                &
                \begin{tabular}{l}
                {\bf Thread 2} \\
                \hline
			\texttt{\flow{if} (\call{\_xbegin}() == \const{STARTED}) \{} \\
			\texttt{~~~~bar++;} \\
			\texttt{~~~~\call{\_xend}();} \\
			\texttt{\} \flow{else} \{} \\
			%\texttt{~~~~\call{mutex\_lock}(\&m);} \\
			\texttt{~~~~\flow{assert}{}(foo + bar < \const{2});} \\
			%\texttt{~~~~\call{mutex\_unlock}(\&m);} \\
			\texttt{\}} \\
                \end{tabular}
        \end{tabular}
        \end{center}
	\caption{Motivating example for retry independence reduction.}
	\label{fig:retry-set-example}
\end{figure}

@@

			& 2,1 & \cpu{28.40} 	& \ints{150} 	& \cpu{26.55}	& \ints{94}	& \cpu{14.88}	& \ints{9} \\

@@

\begin{table}[t]
	\begin{center}
		\footnotesize
		\begin{tabular}{cc}
		\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf STM ({\tt -A -S})} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em est.}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.41} & \ints{4} \\
			({\tt spinlock})
			& 2,2 & \cpu{198.77} & \ints{1702} \\
			% if lock(spin_fixed) will time out on 2,3 and 3,2, this is guaranteed to aswell
			& 3,1 & \cpu{35.28} & \ints{246} \\
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.55} & \ints{4} \\
			({\tt spin\_fixed})
			& 2,2 & \cpu{105.57} & \ints{998} \\
			& 2,3 & \ETAdag{33h 13m} & \ETAdag{321553} \\
			% [JOB 4] progress: 138911/321553 brs (43.200015%), ETA 23h 12m 50s (elapsed 9h 59m 48s)
			% total CPU time consumed: 10h 4s (36004577784 usecs) (core saturation: 12%)
			& 3,1 & \cpu{28.27} & \ints{186} \\
			& 3,2 & \ETAdag{13y 281d} & \ETAdag{1443676} \\
			% [JOB 4] progress: 169893/1443676 brs (11.768080%), ETA 13y 280d 17h 30m 54s (elapsed 9h 59m 48s)
			& 4,1 & \ETAdag{16h 26m} & \ETAdag{432628} \\ % was: 30408, 282084 pre mkrun
			% [JOB 4] progress: 286910/432628 brs (66.317896%), ETA 6h 26m 25s (elapsed 9h 59m 48s)
			% total CPU time consumed: 10h 4s (36004288982 usecs) (core saturation: 12%)
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.44} & \ints{4}		\\
			({\tt mutex})
			& 2,2 & \cpu{16.83} & \ints{180}	\\
			& 2,3 & \cpu{405.21} & \ints{9372}	\\
			& 2,4 & \cpu{24999.68} & \ints{489480}	\\ % was: 15266 sec 384512 pre mkrun
			% total CPU time consumed: 6h 56m 39s (24999680839 usecs) (core saturation: 12%)
			& 3,1 & \cpu{15.00} & \ints{132}	\\
			%& 3,2 & \cpu{29432.87} & \ints{707086}	\\ % pre mkrun fix (let alone bottom1)
			& 3,2 & \ETAdag{26h 42m} & \ETAdag{1223955} \\
			% [JOB 2] progress: 714882/1223955 brs (58.407517%), ETA 16h 41m 58s (elapsed 9h 59m 55s)
			% total CPU time consumed: 10h 3s (36003621109 usecs) (core saturation: 12%)
			& 4,1 & \cpu{665.89} & \ints{15064}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.25} & \ints{1}	\\
			({\tt spin\_fixed})
			& 9,9 & \cpu{4.61} & \ints{1}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.19} & \ints{1}	\\
			({\tt mutex})
			& 9,9 & \cpu{4.62} & \ints{1}	\\
			\end{tabular}
			&
			\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf Non-transactional} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt avl\_mutex}
			& 2,1 & \cpu{3.48} & \ints{7} \\
			& 2,2 & \cpu{6.25} & \ints{85} \\
			& 2,3 & \cpu{24.69} & \ints{561} \\
			& 2,4 & \cpu{217.98} & \ints{4984} \\
			& 3,1 & \cpu{8.26} & \ints{129} \\
			& 3,2 & \cpu{1403.46} & \ints{30653} \\
			& 3,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{199.96} & \ints{4488} \\
			& 4,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			\cline{1-4}
			{\tt map\_mutex}
			& 2,1 & \cpu{39.81} & \ints{83} \\
			& 2,2 & \ETAdag{26h 21m} & \ETAdag{1085126} \\
			% [JOB 9] progress: 496530/1085126 brs (45.757812%), ETA 16h 21m 0s (elapsed 9h 59m 38s)
			% total CPU time consumed: 10h 19s (36019507965 usecs) (core saturation: 12%)
			& 3,1 & \ETAdag{173d 17h} & \ETAdag{12572187} \\
			% [JOB 9] progress: 496281/12572187 brs (3.947451%), ETA 173d 6h 38m 55s (elapsed 9h 59m 43s)
			% total CPU time consumed: 10h 20s (36020148608 usecs) (core saturation: 12%)
			\\
			\\
			\\
			\\
			\\
		\end{tabular}
		\\
		\\
		(a) Verifying HTM locks alone.
		&
		(b) Verifying the lock's client code.
		\end{tabular}
	\end{center}
	\caption{Continuation of Table~\ref{tab:tm-verifs},
		demonstrating abstraction reduction \cite{dbug-phdthesis}
		on the {\tt avl\_fixed} and {\tt map\_basic} tests
		by verifying HTM mutex implementations separately.
		Tested with STM semantics, as both lock implementations include a retry loop.}
	\label{tab:tm-verifs2}
\end{table}
